Fail Faster

### 2025-03-21 paper/paper.tex
decouple ocaml and scala

\section{Evaluation}
\label{section:eval}
% \jwc{Initial section here about eval}\tr{todo}
To assess the impact of our interventions, we evaluate the raw generator performance and bug-finding speed of
\name generators across a range of benchmarks. Our experiments compare generators
built using our technique---with and without \csplitmix \jwc{this is the first mention of csplitmix!}---against those implemented with
existing generator libraries and their default randomness mechanisms. Specifically,
we implement semantically
equivalent staged generator libraries that replicate the behavior of \bq
in OCaml and ScalaCheck in Scala, allowing us to assess the effectiveness of our
technique across different languages and runtime
environments.\bcp{This says ``assess the impact'' twice...}

This section presents our experimental setup, and address the following research questions:

@@

\subsection{Benchmarking Generator Speed}
\label{subsection:benchmarking}
To answer \textbf{RQ1}, we microbenchmark generators, comparing generators in \camlname to semantically identical ones in \bq,
and generators in \scalaname to those in ScalaCheck.
 We vary the choice of \rand in our \camlname generators, using both \bq's default
\texttt{splittable\_random} and our improved SplitMix (\csplitmix), as discussed
in \secref{subsection:faster-rng}.

For \camlname, our test cases consist of generators for boolean lists, binary search trees (BST), and simply
typed lambda calculus (STLC) terms. We implement generators for these benchmarks
variety of \textit{strategies}, varying in structure and
sophistication. These include type-derived generators for BSTs and STLC terms,
using the approach outlined in \secref{subsection:type-derived}; two custom BST
generators, one that repeatedly inserts values into an initially empty tree and
one that materializes the tree in a single pass by generating keys, values, and
subtrees at each step; a generator of boolean lists that operates similarly to
the single-pass BST strategy; and a generator of STLC terms that is correct by construction (``well-typed''), whose behavior is the most complex.
For evaluating \scalaname, we implement a subset of the aformentioned
strategies---the boolean list generator, single-pass BST generator, and
well-typed STLC term generator.

@@

\tr{We might put a graph of calls to generator library functions vs. speedup here, but
I'm not sure it's worth it---thoughts?}

>>>>

\section{Evaluation}
\label{section:eval}
% \jwc{Initial section here about eval}\tr{todo}
We evaluate the raw generator performance and bug-finding speed of
\name generators across a range of benchmarks. Our experiments compare generators
built using our technique---with and without our improved SplitMix (``\csplitmix'')---against those implemented with
existing generator libraries and their default randomness mechanisms. Specifically,
we implement semantically
equivalent staged generator libraries that replicate the behavior of \bq
in OCaml and ScalaCheck in Scala, allowing us to assess the effectiveness of our
technique across different languages and runtime
environments.

This section presents our experimental setup, and addresses the following research questions:

@@

\subsection{Benchmarking Generator Speed}
\label{subsection:benchmarking}
To answer \textbf{RQ1}, we microbenchmark generators, comparing generators in \camlname to semantically identical ones in \bq,
and generators in \scalaname to those in ScalaCheck.
 We vary the choice of \rand in our \camlname generators, using both \bq's default
\texttt{splittable\_random} and \csplitmix, as discussed
in \secref{subsection:faster-rng}. Our test cases consist of generators for boolean lists, binary search trees (BST), and simply
typed lambda calculus (STLC) terms. We implement generators for these benchmarks
variety of \textit{strategies}, varying in structure and
sophistication.

\subsubsection{OCaml}
\label{subsubsection:ocaml}

In \camlname, our strategies include type-derived generators for BSTs and STLC terms
using the approach outlined in \secref{subsection:type-derived}; two custom BST
generators, one that repeatedly inserts values into an initially empty tree and
one that materializes the tree in a single pass by generating keys, values, and
subtrees at each step; a generator of boolean lists that operates similarly to
the single-pass BST strategy; and a generator of STLC terms that is correct by construction (``well-typed'').

@@

\subsubsection{Scala 3}
In \scalaname, we implement a subset of the \camlname
strategies: the boolean list generator, single-pass BST generator, and
well-typed STLC term generator. ScalaCheck does not support type derivation,
so those strategies are excluded.
